Word Learning as Network Growth: A Cross-linguistic Analysis

### 2019-01-09 cogsci/cogsci.Rmd
new modif on manuscript

    "Stager and Werker (1997) first showed that chidlren's early ability to distinguish similar sounds do not automatically translate into word learning skills. Early explanations proposed that children may not be able to encode subtile phonetic contrasts when learning novel word meanings, thus suggesting a binary/discontinuous pattern of development. However, later work has revealed (e.g., through using simpler testing methods) that children do encode such contrasts, thus favoring a rather probabilitic/continuous pattern of development. The present study proposes a precise probabisitic model describing how development may processd in a continuous fashion. The purpose of the model is to account for previousely documented facts while providing new predictions.  We collected data from both preschool children and adults, and we show that the model can explain various patterns of learning both within the same age and across development. More generally, our work highlight the role of computational modeling in advancing our understanding of development through both organizing exsinting knowledge and generating new principled hypotheses."

@@

Regardless of the exact explanation, it is generally accepted that by around 17 m.o, chidlren succeed under the same circumstances [@werker2002]. What could be the mechanism of development? On one possible account, learning is stage-like: younger children learn a single, underspecified representation of similar words (e.g., "bin"/"din"). Development occurs when children specify this intial coarse reprepsentation and learn two distinct catgories. On an other account, learning is continuous: distinct represetations are learned even by younger children, but these representations are encoded with higher uncertainty in youger children, leading to apparent failure in relatively demanding tasks. Development is a continuous process whereby the intinial noisy representations become more precise [see also, @swingley2007].

Experimental evidence suggest a probabilsitic/continuous, rather than a binary/discontinuous develomental scenario. On the one hand, 14-month-olds who typically fail in the original task succeed both when an easier testing method is used [@yoshida2009], and when uncertainty is mitigated via disambiguating cues [@thiessen2007; @dautriche2015]. On the other hand, adults show patterns of learning similar to those shown by 14-month-olds when the task is more challenging and when similarity between words increases [@white2013; @pajak2016].

Here talk about the continuous hypothesis a bit later here. after introducing the experimental evidecne.

Also talk more about the major assumption of model, what is contiuous about him? and what is the source of this hypothsis (swingley, Yoshida, ...)

In the light of these evidence, the purpose of the current work is to propose a precise probabilsitc model of the Stager and Werker's task where developmment is understood to proceed in a continuous fashion across the lifespan. We use this model to both provide a unifying account for documented experimental findings, and to make new predicitions that have not been tested before. Using new data collected from both preschool children and adults, we show that the model can explain various patterns of learning both within the same age and across development.

<!-- The paper is organized as follows. First we present the model and explain how it can be used to make precise predictions about learning and development in the context of Stager and Werker's task. -->

We model the word learning task introduced by @stager1997, and a testing method similar to the one used by @yoshida2009. In this task, particiants are first exposed to the association between pairs of nonesense words (e.g., "lif"/"neem") and pairs of objects. After this exposure phase, participants perform a series of two-alternative forced choices. In each testing trial, one of the two sounds is uttered (e.g., “lif”) and participants choose the corresponding object from the two alternatives. An overview of the task is shown in Figure\ \@ref(fig:task).

Our model consists of a set of variables describing the general process of spoken word recognition in a referential situation. These variables are related in a way that refelects the simple generative scenario represented graphically in Figure\ \@ref(fig:model). When a speaker utters a sound in the presence of an object, the observer assumes that the object $o$ activated the concept $C$ in the speaker's mind. The concept prompted the cooresponding label $L$. Finally, the label was physically instantiated by the sound $s$.

A similar probabilsitic structure was used by @lewis2013 to model concept learning, and by @hofer2017 to model spoken word learning. However, the first study assumed that the sounds are heard unambiguousely, and the second assumed the concepts are observed unambiguously. In our model, we made the more reaistic assumption of ambiguity at the level of both the sounds and the objects. For simplicity, we assume that the probability of membership of objects and sounds to concepts and labels, respectively, are normally distributed:

$$ p(o | C) \sim  \mathcal{N}(\mu_C, \sigma^2_C) $$
$$ p(s| L) \sim  \mathcal{N}(\mu_L, \sigma^2_L) $$
We assume there to be one-to-one mappings between concepts and labels, and that observers have successfully learned these mappings during the exposure phase:
$$
P(L_i|C_j) = 
\begin{cases}
  1 & \text{if  }  i=j \\  
  0  & \text{if  }  i\neq j 
\end{cases}
$$

During the testing phase, participants are presented with one target sound $s_T \in\{s_1, s_2\}$ and the two objects $o_1$ and $o_2$ presented during the learning phase. In order to make a choice, we determine which object is more probable under the target sound $s_T$, in other words, we compare the the probabilities $P(o_1|s_T)$ and $P(o_2|s_T)$. The values of these probabilities can be computed by summing over all possible concepts and labels:
$$P(o|s)=\sum_{C,L} P(o, C, L| s) \propto \sum_{C,L} P(o, C, L, s) $$
The joint probability $P(o, C, L, s)$ is obtained by factoring the bayesian network in Figure 2:
$$P(o,C,L,s) = P(s|L)P(L|C)P(C|o)P(o) $$
which could be tansformed using Bayes rule into:

$$P(o,C,L,s) = P(s|L)P(L|C)P(o|C)P(C) $$
Finally, assuming that the concept prior probability is uniformly ditributed, we obtain the following expression, where all conditional dependencies have been defined in the previous sub-section.

\begin{equation}
P(o|s) = \frac{\sum_{C,L} P(s|L)P(o|C)P(L|C)}{\sum_{o} \sum_{C,L} P(s|L)P(o|C)P(L|C)}
\end{equation}

From the general expression (1) we derive the exact analytical formula which expresses the probability of accurate responses in the testing phase (Figure 1).

```{r model, fig.env = "figure", fig.pos = "h", fig.align='center', fig.width=3.5, fig.height=2.5, fig.cap = "\\label{fig:model}Graphical representation of our model. Circles indicate random variables (shading indicates observed variables). The squares indicates fixed model parameters."}

We provide an intuitive illustration of how this probabilistic account explain patterns of learning and development in Figure XX. Low accuracy in word learning occurs when the perceptual distance between the labels is small relative to the uncertainty with wich these labels are encoded. For example, in Stager and Werker's orginal experiment, children are supposed to associate lable 1 ("bih") and label 2 ("dih") with object 1 and object 2, respectively.  Though children could learn that the label "bih" is a better match to object 1 than "dih", they could still judge the sound "dih" as a plausible instance of the lable "bih", thanks to the relatively large variance/tolerance of the encoding.

Accuracy is high when the perceptual distance between the labels is large relative to the uncertainty of their encoding. Thus, improvement can occur in the same developmental stage if the perceptual distance of the labels is enhanced either through using different-sounding labels (e.g., "lif" vs. "neem" instead of "bih" and "dih") or through using additional disambiguating cues [e.g., @thiessen2007].  Accuracy improves over development because the encoding's uncertainty itself is reduced.

In order to have a more quantitative understanding of the mdoel, we simulate the values of the predicted accuracy (Expression 2) as a function of the perceptual distance between the sounds $\Delta s$. We used as parameters the two remaning variables, i.e., the visual distance between the semantic referents $\Delta o$ and the standard deviation of the dsitributions $p(s| L)$ and $p(o | C)$ (which, in this simulation, have similar values, i.e., $\sigma =\sigma_C \approx \sigma_L$). The simulations are shown in Figure 3.
```{r }

```{r simulation, fig.env = "figure*", fig.pos = "h", fig.width=7, fig.height=3, fig.align = "center", strip.white=TRUE, fig.cap = "\\label{fig:simulation}The predicted probability of accurate responses in the task of learning two similar-sounding words, as a function the perceptual distance between the sounds. Colors indicate different values of the standard deviation which we assume is common to both the label and concept probabilistic representations. Panels represent graphs using different values of the visual distance between the objects."}
plot_simulation
#img <- png::readPNG("figs/data_all.png")
#grid::grid.raster(img)

2) For fixed values of $\Delta s$ and $\Delta o$, accuracy increases when the representational noise (characterized with $\sigma$) decreases. This fact may explain development, i.e., youger children have noisier representations [@swingley2007; @yoshida2009], which leads to lower word recognition accuracy, especially for similar sounding words.

@@

```{r illus, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=3.5, fig.height=2.5, fig.cap = "\\label{fig:illus} An illustration of how a probabilsitic account (where distinct categories are encoded with different degrees of uncertainty) can explain patterns of learning and development. Accuracy experesses the extent to which a given sound instance indicates a unique category. The values vary between 0.5 (total overlap) and 1 (no overalp). Accuracy is low when the perceptual distance between labels is small relative to the category variance. Accuracy increases when the perceptual distance is enhanced (through disambiguation), or when the variance decreases (e.g., through development)."}

illus_plot
```
<!--
To illustrate, imagine that $S_T = S_1$, expression XX leads to:
$$P(O_1 | S_1) \propto P(S_1|L_1)P(O_1| C_1) + P(S_1|L_2)P(O_1| C_2)$$ 
$$P(O_2 | S_1) \propto P(S_1|L_1)P(O_2| C_1) + P(S_1|L_2)P(O_2| C_2)$$

This formula explain why learners may still struggle with learning the meaning of similar words even if they learn the correct mappings. Indeed, one can learn that the sound $S_1$ is a better match to

Yet infants could have learned that bih is a better match to the ‘bih’ object than dih without triggering greater looking to the switch; the similar word could be judged to be a plausible instance of the newly learned label
-->

<!--How do children acquire words? An important step consists in mapping a phonological form (e.g. the sound "cat") to a semantic referent (the concept CAT). A large body of work has been devoted to explore the mechanism of this mapping (Markman, 1990; Smith and Yu, 2008). However, words do not exist in a vacuum; they are organized into a strcuture based on both semantic and phonological similarity principles (e.g., Collins & Loftus, 1975; Luce & Pisoni, 1998), and, though this similarity structure influnces word recognition (Goldinger, Luce & Pisoni, 1989; McNamara, 2006; Arias-Trejo & Plunkett, 2010; Mani & Plunkett, 2011).

@@

In this experiment, we tested participants in the word learning task introduced above (Figure 1). We explored all three parameters of the model. Both the sound similarity ($\Delta s$) and object similarity ($\Delta o$) were varied simulataneousely in a within-subject design. Besides, two age groups (preschool children and adults) were tested on the same task to explore whether development can be characteized with the degree of uncertainty, $\sigma$, in the probabilsitic representations.
<!--Children were trained to learn the association between pairs of nonesense words (e.g., "lif"/"neem") and pairs of objects (e.g., two flowers). After training, children performed a series of two-alternative forced choices. In each testing trial, one of the two sounds is uttered (e.g., “lif”) and participants choose the corresponding object from the two alternatives (e.g., flower 1 or flower 2). Each child learned an artificial lexicon where both the pairs of sounds and the pairs of objects can be similar or different. Our predictions were as follows. If the sound and meaning interact in word learning, then the pair of words that differ on both the meaning and sound levels should be the easiest to learn, followed by the pairs of words that are different on one level, but similar on another level. Finally, the pair of words that are similar on both levels should be the most difficult to learn.  -->

@@

### Participants
We planned to recruit a sample of 60 children ages 4-5 years from the Bing Nursery School on Stanford University’s campus. So far, we collected data from N=47 children (mean age= months, F=). An additional 28 children participated but were removed from analyses because they were not above chance on the catch trials (as was specified in the pre-registration\footnote{https://osf.io/jrh38/}). We also collected a planed sample of N=30 adults on Amazon Mechanical Turk. N=2 adult participants were excluded because of low scores on the catch trials (see pre-registration).

### Stimuli and similarity rating
The sound stimuli were generated using the MBROLA Speech Synthesizer [@dutoit1996]. We generated three kinds of sound pairs which varied in their degree of similarity to English speakers: 1) "different": "lif"/"neem" and "zem"/"doof", 2) "intermediate": "aka"/"ama" and "ada"/"aba", and 3) "similar" non-English minimal pairs: "ada"/"a\textipa{d\super h}a" (in hindi) and "a\textipa{Q}a"/"a\textipa{\textcrh}a" (in arabic).

As for the objects, we used the Dynamic Stimuli javascript library\footnote{https://github.com/erindb/stimuli} which allowed us to generate objects in four different categories: "tree", "bird", "bug", and "fish". These categories are supposed to be naturally occuring kinds that might be seen on an alien planet. In each category, we generated "different", "intermediate" and "similar" levels of similarity by manipuating a continuous property controling features of the category's shape (e.g, body strech and head fatness).

In a separate survey, $N=20$ participants recruited on Amazon Mechanical Turk evaluated the similarity of each sound and objcet pair on a 7-point scale. We computed averge ratings across partcipants, and we normalized the data so that the values vary between 0 to 1.  Results are shown in Figure XX, for each stimuli group. This data will be used in the models as the perceptual distance of sound pairs ($\Delta s$) and object pairs ($\Delta o$).

@@

###Design 
Each age group saw only two of the three levels of similarity described in the previous sub-section: "different" vs. "intermediate" for preschoolers, and "intermediate" vs. "similar" for adults. The experiment consisted of four conditions which involved, each, one pair of sounds-objects associations. These conditions were constructed by crossing the sound's degree of similarity with the object's degree of similarity leading to a 2x2 factorial design in each age group. Besides the 4 conditions, we also tested participants on a fifth catch condition which was similar in its stucture to the other ones, but was used only to select participant who were able to follow the instructions and show minimal learning.

@@

Preschoolers were asked if they would be willing to play a game on a tablet with the experimenter and were informed that they could stop playing at any time. The experimenter explained that the game consisted in learning some words spoken in an alien planet. The experiment began with two simple examples (not included in the analysis), and in these examples children were given feedback from the experimenter so as to make sure they correctly understood the structure of the task. After the introduction and examples, children were tested in a sequence of five conditions: the four experimental conditions plus the catch condition. In each condition, participants saw a first block of four exposure trials followed by four testing trials, and a second block of two exposure trials (for memory refreshment) follwoed by an additional four testing trials.

@@

The procedure for preschoolers and adults were identical except that preschoolers were accompagnied by an experimenter and used a tablet, whereas adults used their local computers to complete the experiment online.

@@

We fit the analystical expression (equation 2) to the participants' responses in each age group.  The values of $\Delta s$ and $\Delta o$ were set based on data from the similarity judgment task (described in the stimuli sub-section). We used two models: \textbf{model 1} fit only one parameter ($\sigma = \sigma_C =\sigma_L$), and \textbf{model 2} fit two parameters ($\sigma_C  \neq \sigma_L$). The values of the parameters were derived using weighted least-squares estimates.

@@

First we analyzed the experimental results shown in Figure (XX, left), using a mixed-effects logistic regression with sound and object distances as fixed effects, and with a maximal random effects strcuture [@barr2013]. Results are shown in Table XX. We found a main effect of sound distance on the accuray of learning in both children and adults, thus replicating previous findings. We also found a main effect of object distance, thus confirming the new prediction of our model.

@@

Figures XX (middle and right graphs) show the predictions of the models. Both model 1 and model 2 fit reseanaby well the experimental data in both children and adults. In particular, they both correcly predict the relative recognition accuacy accross conditions: the pair of words that differ on both the object and sound levels were the easiest to learn, followed by the pairs of words that differ on only one level, then the pair of words that are similar on both levels.

For Model 1, the fitted noise parameter was $\sigma =$ `r round(mod1_val$val[which(mod1_val$group=="children")],2)` [`r round(mod1_val$lower[which(mod1_val$group=="children")],2)`, `r round(mod1_val$upper[which(mod1_val$group=="children")],2)`] for preschoolers, and $\sigma =$ `r round(mod1_val$val[which(mod1_val$group=="adults")],2)` [`r round(mod1_val$lower[which(mod1_val$group=="adults")],2)`, `r round(mod1_val$upper[which(mod1_val$group=="adults")],2)`] for adults. It explained the majority of the variance ($R^2=$ `r R2_model1`). For model 2, children had a sound specific noise of $\sigma_S =$ `r round(mod2_val$val[which(mod2_val$group=="children" & mod2_val$param=="Vr_s")],2)` [`r round(mod2_val$lower[which(mod2_val$group=="children" & mod2_val$param=="Vr_s")],2)`, `r round(mod2_val$upper[which(mod2_val$group=="children" & mod2_val$param=="Vr_s")],2)`], and a concept specific noise of $\sigma_C =$ `r round(mod2_val$val[which(mod2_val$group=="children" & mod2_val$param=="Vr_o")],2)` [`r round(mod2_val$lower[which(mod2_val$group=="children" & mod2_val$param=="Vr_o")],2)`, `r round(mod2_val$upper[which(mod2_val$group=="children" & mod2_val$param=="Vr_o")],2)`]. Adults had a sound specific noise of $\sigma_S =$ `r round(mod2_val$val[which(mod2_val$group=="adults" & mod2_val$param=="Vr_s")],2)` [`r round(mod2_val$lower[which(mod2_val$group=="adults" & mod2_val$param=="Vr_s")],2)`, `r round(mod2_val$upper[which(mod2_val$group=="adults" & mod2_val$param=="Vr_s")],2)`]. The model explain almost all the variance ($R^2=$ `r R2_model2`), and a concept specific noise of $\sigma_C =$ `r round(mod2_val$val[which(mod2_val$group=="adults" & mod2_val$param=="Vr_o")],2)` [`r round(mod2_val$lower[which(mod2_val$group=="adults" & mod2_val$param=="Vr_o")],2)`, `r round(mod2_val$upper[which(mod2_val$group=="adults" & mod2_val$param=="Vr_o")],2)`]. Note that, despite the fact that Model 1 used only one degree of freedom, it captures the data variance almost as well as Model 2 which used two degrees of freedom.

@@

Discuss Hofer & Levy, 2017, and Fourtassi & Frank, 2017

>>>>

    "Stager and Werker (1997) first showed that chidlren's early ability to distinguish similar sounds do not automatically translate into word learning skills. Early explanations proposed that children may not be able to encode subtile phonetic contrasts when learning novel word meanings, thus suggesting a discontinuous/stage-like pattern of development. However, later work has revealed (e.g., through using simpler testing methods) that children do encode such contrasts, thus favoring a rather a continuous pattern of development. The present study proposes a precise probabisitic model describing how development may processd in a continuous fashion. The purpose of the model is to account for previousely documented facts while providing new predictions.  We collected data from both preschool children and adults, and we show that the model can explain various patterns of learning both within the same age and across development. Our work highlight the role of computational modeling in advancing our understanding of development through both organizing exsinting knowledge and generating new principled hypotheses."

@@

Regardless of the exact explanation, it is generally accepted that by around 17 m.o, children succeed in the same task [@werker2002]. What could be the mechanism of development? Early acccounts assumed–whether implcitly or explicitly– that children encode words in a binary way: they either fail or succeed in encoding the relevant phonetic details (simulataneousely with the meanings). This account suggested a discontinuous/stage-like pattern of development whereby younger children fail to encode the contrastive phonetic detail, whereas older children succeed.

Nevertheless, subsequent findings suggest otherwise. On the one hand, 14-month-olds–who typically fail in the original task–succeed when an easier *testing* method is used, even under the same *learning* conditions [@yoshida2009]. They also succeed when uncertainty is mitigated via disambiguating cues [e.g., @thiessen2007]. On the other hand, adults show patterns of learning similar to those shown by 14-month-olds when the task is more challenging and when similarity between words increases [@white2013; @pajak2016].

These evidence point towards another scenario, where the representations are encoded in a probablistic (rather than binary) way, and where development is continuous, rather than stage-like [@swingley2007; @yoshida2009; @pajak2016; @hofer2017]. On this account, correct represetations are learned early in development, but these representations are encoded with higher uncertainty in youger children, leading to apparent failure in relatively demanding tasks. Development is a continuous process whereby the intinial noisy representations become more precise. Crucially, more precise representation are still imperfect, as low accuracy learning can be obtained even with adults when the sounds are subtle enough, e.g., non-native sounds [@pajak2016].

We provide an intuitive illustration of how such an account explains patterns of learning and development in Figure \ref{fig:illus}. We observe low accuracy in word learning when the perceptual distance between the labels is small relative to the uncertainty/tolerance with wich these labels are encoded. For example, in Stager and Werker's orginal experiment, children are supposed to associate lable 1 ("bih") and label 2 ("dih") with object 1 and object 2, respectively.  Though children could learn that the label "bih" is a better match to object 1 than "dih", they could still judge the sound "dih" as a plausible instance of the lable "bih", thanks to the relatively large tolerance of the encoding.

Accuracy in word learning increases when the perceived distance between the labels is large relative to the tolerance of their encoding. This improvement can occur in the same developmental stage if the perceptual distance between labels is enhanced through using different-sounding labels (e.g., "lif" vs. "neem" instead of "bih" and "dih") or through using contextual cues [@thiessen2007; @rost2009]. Besides, accuracy can improve across development through the refinement of the encoding, i.e., if the uncertainy of the encoding decreases.

Building on this intuition, the current work proposes a precise probabilsitc model, which we use to both account for previous experimental findings, and to make new predicitions that have not been tested before. Using new data collected from both preschool children and adults, we show that the model can explain various patterns of learning both within the same age and across development.

@@

```{r illus, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=3.5, fig.height=2.5, fig.cap = "\\label{fig:illus} An illustration of the probabilsitic account of similar word learning using simulated data. Words are category distributions over the perceptual space, encoded with different degrees of uncertainty. Accuracy experesses the extent to which a given sound instance indicates a unique underlying category. The values vary between 0.5 (total overlap between the distributions) and 1 (no overalp). Accuracy is low when the perceptual distance between labels is small relative to the category variance. Accuracy increases when the perceptual distance is enhanced (through disambiguation), or when the variance decreases (e.g., through development)."}

illus_plot
```

We model the word learning task introduced by @stager1997, and a testing method similar to the one used by @yoshida2009. In this task, particiants are first exposed to the association between pairs of nonesense words (e.g., "lif"/"neem") and pairs of objects. After this exposure phase, participants perform a series of two-alternative forced choices. In each testing trial, one of the two sounds is uttered (e.g., “lif”) and participants choose the corresponding object from the two alternatives. An overview of the task is shown in Figure \ref{fig:task}.

Our model consists of a set of variables describing the general process of spoken word recognition in a referential situation. These variables are related in a way that refelects the simple generative scenario represented graphically in Figure \ref{fig:model}. When a speaker utters a sound in the presence of an object, the observer assumes that the object $o$ activated the concept $C$ in the speaker's mind. The concept prompted the corresponding label $L$. Finally, the label was physically instantiated by the sound $s$.

A similar probabilsitic structure was used by @lewis2013 to model concept learning, and by @hofer2017 to model spoken word learning. However, the first study assumed that the sounds are heard unambiguousely, and the second assumed the concepts are observed unambiguously. In our model, we assume there to be ambiguity at the level of both the labels and the concepts. For simplicity, we assume that the probability of membership of objects and sounds to concepts and labels, respectively, are normally distributed:

$$ p(o | C) \sim  \mathcal{N}(\mu_C, \sigma^2_C) $$
$$ p(s| L) \sim  \mathcal{N}(\mu_L, \sigma^2_L) $$
Finally, we assume there to be one-to-one mappings between concepts and labels, and that observers have successfully learned these mappings during the exposure phase:
$$
P(L_i|C_j) = 
\begin{cases}
  1 & \text{if  }  i=j \\  
  0  & \text{if  }  i\neq j 
\end{cases}
$$

<!--If we denote the correct/target object as $o_T$ and the incorrect object as $o_{\lnot T}$, then the probability of chosing the correct object is: $P(o_T|s_T) = $ -->

During the testing phase (Figure \ref{fig:task}), participants are presented with one target sound $s_T \in\{s_1, s_2\}$ and with both objects $o_1$ and $o_2$. In order to make a choice, we need to determine which object is more probable under the target sound $s_T$. In other words, we need to compare the probabilities $P(o_1|s_T)$ and $P(o_2|s_T)$. The values of these probabilities can be computed by summing over all possible concepts and labels:
$$P(o|s)=\sum_{C,L} P(o, C, L| s) \propto \sum_{C,L} P(o, C, L, s) $$
The joint probability $P(o, C, L, s)$ is obtained by factoring the Bayesian network in (Figure \ref{fig:model}):
$$P(o,C,L,s) = P(s|L)P(L|C)P(C|o)P(o) $$
which could be tansformed using Bayes rule into:

$$P(o,C,L,s) = P(s|L)P(L|C)P(o|C)P(C) $$
Finally, assuming that the concepts' prior probability is uniformly ditributed\footnote{This is a reasonable assumption given the similarity of the concepts used in each naming situation. See the stimuli sub-section in the Experiment below.}, we obtain the following expression, where all conditional dependencies are now well defined:

$$
P(o|s) = \frac{\sum_{C,L} P(s|L)P(o|C)P(L|C)}{\sum_{o} \sum_{C,L} P(s|L)P(o|C)P(L|C)}
$$

From this general expression we derive the exact analytical formula, which expresses the probability of accurate responses in the testing phase of the task:

```{r model, fig.env = "figure", fig.pos = "t", fig.align='center', fig.width=3.5, fig.height=2.5, fig.cap = "\\label{fig:model}Graphical representation of our model. Circles indicate random variables (shading indicates observed variables). The squares indicates fixed model parameters."}

In order to have a more quantitative understanding of the model, we simulate the values of the predicted accuracy (Expression 1) as a function of the perceptual distance between the sounds $\Delta s$. We used as parameters the two remaning variables, i.e., the visual distance between the semantic referents $\Delta o$ and the standard deviation of the dsitributions $p(s| L)$ and $p(o | C)$ (which, in this simulation, are assumed to have similar values, i.e., $\sigma =\sigma_C \approx \sigma_L$). The simulations are shown in Figure \ref{fig:simulation}.
```{r }

```{r simulation, fig.env = "figure*", fig.pos = "h", fig.width=7, fig.height=3, fig.align = "center", strip.white=TRUE, fig.cap = "\\label{fig:simulation}The predicted probability of accurate responses in the testing phase, as a function the perceptual distance between the sounds. Colors indicate different values of the standard deviation which we assume is common to both the labels' and concepts' probabilistic representations. Panels represent graphs using different values of the visual distance between the objects."}
plot_simulation
#img <- png::readPNG("figs/data_all.png")
#grid::grid.raster(img)

2) For fixed values of $\Delta s$ and $\Delta o$, accuracy increases when the representational uncertainty (characterized with $\sigma$) decreases. This fact may explain development, i.e., youger children have noisier representations [see @swingley2007; @yoshida2009], which leads to lower word recognition accuracy, especially for similar-sounding words.

@@

In this experiment, we tested participants in the word learning task introduced above (Figure \ref{fig:task}). We explored all three parameters of the model. In particular, both the sound similarity ($\Delta s$) and object similarity ($\Delta o$) were varied simulataneousely in a within-subject design. Besides, two age groups (preschool children and adults) were tested on the same task to explore whether development can be characteized with the uncertainty parameter, $\sigma$, in the probabilsitic representations.
<!--Children were trained to learn the association between pairs of nonesense words (e.g., "lif"/"neem") and pairs of objects (e.g., two flowers). After training, children performed a series of two-alternative forced choices. In each testing trial, one of the two sounds is uttered (e.g., “lif”) and participants choose the corresponding object from the two alternatives (e.g., flower 1 or flower 2). Each child learned an artificial lexicon where both the pairs of sounds and the pairs of objects can be similar or different. Our predictions were as follows. If the sound and meaning interact in word learning, then the pair of words that differ on both the meaning and sound levels should be the easiest to learn, followed by the pairs of words that are different on one level, but similar on another level. Finally, the pair of words that are similar on both levels should be the most difficult to learn.  -->

@@

### Participants
We planned to recruit a sample of 60 children ages 4-5 years from the Bing Nursery School on Stanford University’s campus. So far, we collected data from N=47 children (mean age= months, F=). An additional 28 children participated but were removed from analyses because they were not above chance on the catch trials (as was specified in the pre-registration\footnote{https://osf.io/jrh38/}). We also collected a sample of N=20 adults on Amazon Mechanical Turk (this is a pilot, I will plan for 60 participants). N=2 adult participants were excluded because of low scores on the catch trials (see pre-registration).
(I still need to write the code that derives these numbers directly from the data).

### Stimuli and similarity rating
The sound stimuli were generated using the MBROLA Speech Synthesizer [@dutoit1996]. We generated three kinds of non-sense word pairs which varied in their degree of similarity to English speakers: 1) "different": "lif"/"neem" and "zem"/"doof", 2) "intermediate": "aka"/"ama" and "ada"/"aba", and 3) "similar" non-English minimal pairs: "ada"/"a\textipa{d\super h}a" (in hindi) and "a\textipa{Q}a"/"a\textipa{\textcrh}a" (in arabic).

As for the objects, we used the Dynamic Stimuli javascript library\footnote{https://github.com/erindb/stimuli} which allowed us to generate objects in four different categories: "tree", "bird", "bug", and "fish". These categories are supposed to be naturally occuring kinds that might be seen on an alien planet. In each category, we generated "different", "intermediate" and "similar" pairs by manipuating a continuous property controling features of the category's shape (e.g, body strech or head fatness).

In a separate survey, $N=20$ participants recruited on Amazon Mechanical Turk evaluated the similarity of each sound and objcet pair on a 7-point scale. We processed the resulting data so that it can be used in the model. We normalized the values with respect to the most distant level, and we scaled them within the range [0,1]. Processed data are shown in Figure \ref{fig:stim}, for each stimuli group. This data will be used in the models as the perceptual distance of sound pairs ($\Delta s$) and object pairs ($\Delta o$).

@@

###Design 
Each age group saw only two of the three levels of similarity described in the previous sub-section: "different" vs. "intermediate" for preschoolers, and "intermediate" vs. "similar" for adults. We made this choice because, on the one hand, adults were at ceiling with "different" sounds, and on the other hand, children were at chance with the "similar" sounds. That said, this difference in the level of similairty is accounted for in the model through using the appropriate perceptual distance for each age group (Figure \ref{fig:stim})

The experiment consisted of four conditions which involved, each, one pair of sounds-objects associations. These conditions were constructed by crossing the sound's degree of similarity with the object's degree of similarity leading to a 2x2 factorial design in each age group. Besides the 4 conditions, we also tested participants on a fifth catch condition which was similar in its stucture to the other ones, but was used only to select participants who were able to follow the instructions and show minimal learning.

@@

Preschoolers were asked if they would be willing to play a game on a tablet with the experimenter and were informed that they could stop playing at any time. The experimenter explained that the game consisted in learning some words spoken in an alien planet. The experiment began with two simple examples (not included in the analysis), and in these examples children were given feedback from the experimenter so as to make sure they correctly understood the structure of the task. After the introduction and examples, children were tested in a sequence of five conditions: the four experimental conditions plus the catch condition. In each condition, participants saw a first block of four exposure trials followed by four testing trials, and a second block of two exposure trials (for memory refreshment) followed by an additional four testing trials.

@@

The procedure adults were identical except to that of preschool children, except that preschoolers were accompagnied by an experimenter and used a tablet, whereas adults used their local computers to complete the experiment online.

@@

We fit the probability function (equation 2) to the participants' responses in each age group.  The values of $\Delta s$ and $\Delta o$ were set based on data from the similarity judgment task (described in the stimuli sub-section). We used two models: \textbf{model 1} fit only one parameter ($\sigma = \sigma_C =\sigma_L$), and \textbf{model 2} fit two parameters ($\sigma_C  \neq \sigma_L$). The values of the parameters were derived using weighted least-squares estimates.

@@

We first analyzed the experimental results shown in Figure (\ref{fig:data_all}, left), using a mixed-effects logistic regression with sound and object distances as fixed effects, and with a maximal random effects strcuture [@barr2013]. Results are shown in Table 1. We found a main effect of sound distance on the accuray of learning in both children and adults, thus replicating previous findings. We also found a main effect of object distance, thus confirming the new prediction of our model.

@@

Figures (\ref{fig:data_all}, middle and right graphs) show the predictions of the models. Both model 1 and model 2 fit reseanaby well the experimental data in both children and adults. In particular, they both correcly predict the relative recognition accuacy accross conditions: the pair of words that differ on both the object and sound levels were the easiest to learn, followed by the pairs of words that differ on only one level, then the pair of words that are similar on both levels.

For Model 1, the fitted noise parameter was $\sigma =$ `r round(mod1_val$val[which(mod1_val$group=="children")],2)` [`r round(mod1_val$lower[which(mod1_val$group=="children")],2)`, `r round(mod1_val$upper[which(mod1_val$group=="children")],2)`]\footnote{95 \% Confidence intervals.} for preschoolers, and $\sigma =$ `r round(mod1_val$val[which(mod1_val$group=="adults")],2)` [`r round(mod1_val$lower[which(mod1_val$group=="adults")],2)`, `r round(mod1_val$upper[which(mod1_val$group=="adults")],2)`] for adults. It explained the majority of the variance ($R^2=$ `r R2_model1`). For model 2, children had a sound specific noise of $\sigma_S =$ `r round(mod2_val$val[which(mod2_val$group=="children" & mod2_val$param=="Vr_s")],2)` [`r round(mod2_val$lower[which(mod2_val$group=="children" & mod2_val$param=="Vr_s")],2)`, `r round(mod2_val$upper[which(mod2_val$group=="children" & mod2_val$param=="Vr_s")],2)`], and a concept specific noise of $\sigma_C =$ `r round(mod2_val$val[which(mod2_val$group=="children" & mod2_val$param=="Vr_o")],2)` [`r round(mod2_val$lower[which(mod2_val$group=="children" & mod2_val$param=="Vr_o")],2)`, `r round(mod2_val$upper[which(mod2_val$group=="children" & mod2_val$param=="Vr_o")],2)`]. Adults had a sound specific noise of $\sigma_S =$ `r round(mod2_val$val[which(mod2_val$group=="adults" & mod2_val$param=="Vr_s")],2)` [`r round(mod2_val$lower[which(mod2_val$group=="adults" & mod2_val$param=="Vr_s")],2)`, `r round(mod2_val$upper[which(mod2_val$group=="adults" & mod2_val$param=="Vr_s")],2)`]. The model explain almost all the variance ($R^2=$ `r R2_model2`), and a concept specific noise of $\sigma_C =$ `r round(mod2_val$val[which(mod2_val$group=="adults" & mod2_val$param=="Vr_o")],2)` [`r round(mod2_val$lower[which(mod2_val$group=="adults" & mod2_val$param=="Vr_o")],2)`, `r round(mod2_val$upper[which(mod2_val$group=="adults" & mod2_val$param=="Vr_o")],2)`]. Interestingly, despite the fact that Model 1 used only one degree of freedom, it captures the data variance almost as well as Model 2 (which used two degrees of freedom).

@@

<!--

How do children acquire words? An important step consists in mapping a phonological form (e.g. the sound "cat") to a semantic referent (the concept CAT). A large body of work has been devoted to explore the mechanism of this mapping (Markman, 1990; Smith and Yu, 2008). However, words do not exist in a vacuum; they are organized into a strcuture based on both semantic and phonological similarity principles (e.g., Collins & Loftus, 1975; Luce & Pisoni, 1998), and, though this similarity structure influnces word recognition (Goldinger, Luce & Pisoni, 1989; McNamara, 2006; Arias-Trejo & Plunkett, 2010; Mani & Plunkett, 2011).
